Bullet Data Preparation for LIME Diagnostics Paper

### 2020-09-23 code/02-data-preparation.Rmd
trying a new filtering method

@@

@@

```{r}
rtrees_pred = predict(bulletxtrctr::rtrees, type = "prob")[,2]
new_pred = predict(bulletxtrctr::rtrees, bullet_train_filtered %>% select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
new_pred_full = predict(bulletxtrctr::rtrees, bullet_train_raw %>% select(rownames(bulletxtrctr::rtrees$importance)[]), type = "prob")[,2]
```

@@

@@

>>>>

The dimensions of the raw data:

```{r}
bullet_train_raw %>% dim()
```

@@

The code below removes observations based on Eric Hare's code (available [here](ttps://github.com/erichare/imaging-paper/blob/master/code/full_run.R)), which he thinks may be the code used to train `rtrees`:

```{r}
bullet_train_eric_filter <- 
  bullet_train_raw %>%
  separate(col = "land_id1", into = c("study1", "barrel1", "bullet1", "land1")) %>%
  separate(col = "land_id2", into = c("study2", "barrel2", "bullet2", "land2")) %>%
  filter(study1 != "Hamby173" | bullet1 != "BE") %>%
  filter(study2 != "Hamby173" | bullet2 != "BE")

# Eric's code for reference:
# filter(study.y != "Hamby44" | barrel.y != "E") %>%
# filter(study.x != "Hamby44" | barrel.x != "E") %>%
```

Here, the dimensions to not agree with the number of observations in `rtrees`:

```{r}
dim(bullet_train_eric_filter)
length(bulletxtrctr::rtrees$predicted) == dim(bullet_train_eric_filter)[1]
```

@@

```{r}
rtrees_pred = predict(bulletxtrctr::rtrees, type = "prob")[,2]

new_pred = predict(bulletxtrctr::rtrees, 
                   bullet_train_filtered %>% 
                     select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]

new_pred_full = predict(bulletxtrctr::rtrees, 
                        bullet_train_raw %>%
                          select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
```

@@

```{r}
bulletxtrctr::rtrees$call
```

@@

Comparison to the data Eric Hare said was used to fit `rtrees` which has half the number of observations as the number of rtrees predictions:

```{r}
eric <- read.csv("https://raw.githubusercontent.com/erichare/imaging-paper/master/data/data-25-25/bullet-stats.csv")
dim(eric)
```
